`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-02-19 analysis/VOCC/3-vocc-temp.Rmd
correct indices for all temp years vocc

  if (years_sampled == 7) indices <- c(1, 1, 1, 2, 2, 2)
  if (years_sampled == 8) indices <- c(1, 1, 1, 1, 2, 2, 2,2)
} else {
  d <- d_all %>%
    filter(year >= start_year) %>%
    filter(year <= start_year + 3)
  unique(d$year)
  indices <- c(1, 2)
  year_range <- 2
}

>>>>

  if (years_sampled == 7) indices <- c(1, 1, 1, 2, 2, 2, 2) # was 6 for some reason?
  if (years_sampled == 8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)
} else {
  d <- d_all %>%
    filter(year >= start_year) %>%
    filter(year <= start_year + 3)
  unique(d$year)
  indices <- c(1, 2)
  year_range <- 2
}
